\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-10 trunk/europa.tex
checkpoint. cleaning up europa's architecture section before diving into modeling.

The Constraint Reasoning Engine (CRE) manages variables, the domains
from which they can take values, and constraints that define
relationships among variables. It also provides an efficient arc
consistency mechanism \cite{mackworth77}. The CRE is designed so that
specialized reasoning algorithms for specific constraints can be easily
and efficiently plugged in. The Plan Database (PDB) manages object types
and objects, which are a mechanism to group variables to more naturally
model the real world in much the same way that object oriented
programming does. Also manages tokens, which are a mechanism to group
variables to represent temporally scoped state. Objects and tokens can
be used to model planning domains in a much more natural and extensible
way that a pure CSP approach can. The Rules Engine (RE) manages token
relationships in a planning model. The language modules (NDDL, ANML, and
other higher level modeling languages) are used to create domain models
and problem instances \comment{point advantages over pure programming
  API approaches, provide snippets}. Finally the API Layer (Fig.
\ref{fig:europa-api}) makes all the services available so that \eu can
be used to build applications.

\comment{Is Fig. \ref{fig:europa-api} necessary?}

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/EUROPA-API.jpg}
\caption{\small EUROPA's Client API}
\label{fig:europa-api}
\vskip+0.1cm
\end{figure}

	% \item Extension Modules bundled with EUROPA: Temporal Network, Resources, NDDL, ANML.
	% 	\begin{enumerate}
	% 		\item Temporal Network
	% 		\item Resources
	% 		\item NDDL
	% 		\item ANML (TODO:maybe it's better to leave out?)
	% 	\end{enumerate}

@@

\item Open Condition: an open condition is an inactive token. Inactive
  tokens can be generated by explicitly posted goals, or when a token is
  activated, rules may fire that create inactive slave tokens (TODO:
  point to more detailed decription above in Rules Engine section). Open
  Conditions can be resolved in three ways:

@@

It should be emphasized that while this algorithm is commonly employed,
it is only one of many that could be implemented. TODO: give examples of
local search solvers for scheduling and CSP?

>>>>

The \textbf{Constraint Reasoning Engine} (CRE) manages domain types, and constraints that define
relationships among variables. It also provides an efficient arc
consistency mechanism \cite{mackworth77}. The CRE is designed so that
specialized reasoning algorithms for specific constraints can be easily
and efficiently plugged in.

The \textbf{Plan Database} (PDB) manages object types
and objects,

The \textbf{Rules Engine} (RE) manages token
relationships in a planning model.

The {Language Modules} (NDDL, ANML, and
other higher level modeling languages) are used to create domain models
and problem instances \comment{point advantages over pure programming
  API approaches, provide snippets}.

  Finally,  the \textbf{API Layer}  makes all the services available so that \eu can
be used to build applications.

Extension Modules bundled with EUROPA: Temporal Network, Resources, NDDL, ANML.
\begin{enumerate}
	\item Temporal Network
	\item Resources
	\\item NDDL. ANML (TODO:maybe it's better to leave out?)
\end{enumerate}

@@

\item Open Condition: an open condition is an inactive token. Inactive
  tokens can be generated by explicitly posted goals, or when a token is
  activated, rules may fire that create inactive slave tokens
  \comment{point to more detailed decription above in Rules Engine
    section}.
  Open
  Conditions can be resolved in three ways:

@@

It should be emphasized that while this algorithm is commonly employed,
it is only one of many that could be implemented. \comment{give examples
  of local search solvers for scheduling and CSP?}
